A studyforrest extension, an annotation of spoken language in the German dubbed movie ``Forrest Gump'' and its audio-description

### 2020-06-02 paper/main.tex
revision of a couplele of to dos

% intro to analysis
We implemented a standard three-level, voxel-wise general linear model (GLM) to
average parameter estimates across the eight stimulus segments, and later across
19 subjects.
% 1st lvl
At the first level analyzing each segment for each subject individually, we
created 26 regressors based on events drawn from the annotation (see Table
\ref{tab:regressors}).
% part-of-speech labels: labels to events, top 20
The 20 most often occurring detailed part-of-speech labels (\texttt{nn} with
N=\rNnAll\space to text{prf} with N=\rPrfAll) were modeled as boxcar function
from onset to offset of each word \todo{This has errors that I do not know how
to fix; sorry, unclear what you mean by that}.
% path-of-speech labels: remaining labels
The remaining other part-of-speech labels were pooled to a single new label
(\texttt{tag\_other}; N=\rTagotherAll) and each event was modeled as a boxcar
function from onset to offset of the corresponding word\todo{I do not know what
this mean; CH: hope it got clearer now}.
% phonemes
The top 80 phonemes (\texttt{n} with N=6053 to \texttt{IY1} with N=32) were
pooled to \texttt{phonemes} (N=\rPhonesAll) and each event modeled as boxcar
function from onset to offset of the corresponding phoneme.\todo{Does that mean
they share events with "other"; CH: dunno what you mean, but text should be
clearer now}.
% sentence (endings)
The end of each complete grammatical sentence was modeled as an impulse event
(N=\rSentenceAll) to capture variance of sentence comprehension\todo{Why? Above
it says 'we tested if similar linguistic concepts providing high semantic
information (proper nouns and nouns)'. What does this need sentences for? CH:
it is kinda nuisance regressor}.
% no-speech intro
``No-speech'' events (\texttt{no-sp}; N=\rNospAll) serving as a control
condition were created by the following rationale: events were fitted into
longer lasting intervals between onsets and offsets of words and thus within
intervals without audible speech \todo{Why assumed? Isn't the point of the
annotation to "know"? CH: words where chosen to carefully; intervals don't
contain any audible speech with >98 perc. certainty}
% minimum distance to words
Each event of the no-speech condition had to have a minimum distance of
\unit[1.8]{s} to an onsets or offsets of a word, and to each onset to another
event of the no-speech condition.
% length of no-speech events
A length of \unit[70]{ms} was chosen for no-speech events matching the average
length of phonemes.
% low-level nuisance regressors
Lastly, we used events\todo{They are not really events, but a continuous
nuisance regressor; CH: okay, how do you phrase that correctly?} reflecting
low-level auditory features (left-right difference in volume and root mean
squared volume) averaged across the length of every movie frame (\unit[40]{ms}).
All events were convolved with FSL's ``Double-Gamma HRF'' as a model of the
hemodynamic response function to create the actual regressors.
% reference to figure ``correlation of regressors''
The Pearson correlation coefficients of the 26 regressors across the time course
of all stimulus segments can be seen in Figure \ref{fig:reg-corr}.
% temporal derivatives
Temporal derivatives were also included in the design matrix and the design was
subjected to the same temporal filtering as the BOLD time series.
% motion parameters
Finally, six motion parameters were used as additional nuisance regressors.

@@

\section*{Conclusions} \todo[inline]{the paper needs to serve a purpose.  One
is, of course, to be documentation for the annotation.  Another is to attract
people to use this work for their own studies.  I would even argue that this is
the \textit{main} purpose, given that the annotation in itself represents to
scientific progress.  The need to give an accurate assessment what this can be
used for and what is problematic or impossible.  ATM this is the only statement
in this regard: 'facilitates modeling of hemodynamic brain responses correlating
with speech-related events' and the only indication of purpose is 'additional
confound measures'.  I think this is incongruent with the amount of work and the
level of detail of this annotation; CH: let's discuss that personally}
% state what you think are the main conclusions that can be realistically drawn
% from the findings in the paper, taking care not to make claims that cannot be
% supported.  intro
As an extension of the studyforrest dataset, we present an annotation of spoken
language in the two hours lasting ``research cut'' of the audio-visual movie
``Forrest Gump'' and its temporally aligned audio-description.
% what we did
We annotated the onset and offset of sentences, words and phonemes, and the
corresponding speaker's identity.
% what for
An additional tagging of each word's linguistic features and the public nature
of the dataset enable independent working groups to create sophisticated models
of hemodynamic activity correlating with speech-related events in a naturalistic
stimulus.
% results
Results of our dataset validating analysis that we run as a proof of concept
show that the annotation's content can indeed / in principle be used to
isolate/track speech-related networks in the human brain under life-like
conditions.

>>>>

% intro to analysis
We implemented a standard three-level, voxel-wise general linear model (GLM) to
average parameter estimates across the eight stimulus segments, and later across
19 subjects.
% 1st lvl
At the first level analyzing each segment for each subject individually, we
created 26 regressors based on events drawn from the annotation (see Table
\ref{tab:regressors}).
% part-of-speech labels: labels to events, top 20
The 20 most often occurring detailed part-of-speech labels (\texttt{nn} with
N=\rNnAll\space to text{prf} with N=\rPrfAll) were modeled as boxcar function
from onset to offset of each word \todo{This has errors that I do not know how
to fix; sorry, unclear what you mean by that}.
% path-of-speech labels: remaining labels
The remaining other part-of-speech labels were pooled to a single new label
(\texttt{tag\_other}; N=\rTagotherAll) and each event was modeled as a boxcar
function from onset to offset of the corresponding word\todo{I do not know what
this mean; CH: hope it got clearer now}.
% phonemes
The top 80 phonemes (\texttt{n} with N=6053 to \texttt{IY1} with N=32) were
pooled to \texttt{phonemes} (N=\rPhonesAll) and each event modeled as boxcar
function from onset to offset of the corresponding phoneme.\todo{Does that mean
    they share events with "other"; CH: dunno what you mean, but text should be
clearer now}.
% sentence (endings)
The end of each complete grammatical sentence was modeled as an impulse event
(N=\rSentenceAll) to capture variance correlating with sentence comprehension.
\todo{Why? Above it says 'we tested if similar linguistic concepts providing
    high semantic information (proper nouns and nouns)'. What does this need
sentences for? CH: it is kinda nuisance regressor}
% no-speech intro
``No-speech'' events (\texttt{no-sp}; N=\rNospAll) serving as a control
condition were created by the following rationale: events were fitted into
longer lasting intervals between onsets and offsets of words and thus within
intervals without audible speech \todo{Why assumed? Isn't the point of the
annotation to "know"? CH: words where chosen to carefully; intervals don't
contain any audible speech with >98 perc. certainty}
% minimum distance to words
Each event of the no-speech condition had to have a minimum distance of
\unit[1.8]{s} to an onsets or offsets of a word, and to each onset to another
event of the no-speech condition.
% length of no-speech events
A length of \unit[70]{ms} was chosen for no-speech events matching the average
length of phonemes.
% low-level nuisance regressors
Lastly, we used events\todo{They are not really events, but a continuous
nuisance regressor; CH: okay, how do you phrase that correctly?} reflecting
low-level auditory features (left-right difference in volume and root mean
squared volume) averaged across the length of every movie frame (\unit[40]{ms}).
All events were convolved with FSL's ``Double-Gamma HRF'' as a model of the
hemodynamic response function to create the actual regressors.
% reference to figure ``correlation of regressors''
The Pearson correlation coefficients of the 26 regressors across the time course
of all stimulus segments can be seen in Figure \ref{fig:reg-corr}.
% temporal derivatives
Temporal derivatives were also included in the design matrix and the design was
subjected to the same temporal filtering as the BOLD time series.
% motion parameters
Finally, six motion parameters were used as additional nuisance regressors.

@@

\todo[inline]{the paper needs to serve a purpose:
    a) documentation for the annotation.
    b) attract people to use this work for their own studies.
    I would even argue that this is the \textit{main} purpose, given that the
    annotation in itself represents to scientific progress. The need to give an
    accurate assessment what this can be used for and what is problematic or
    impossible.  ATM this is the only statement in this regard: 'facilitates
    modeling of hemodynamic brain responses correlating with speech-related
events' and the only indication of purpose is 'additional confound measures'. I
thin this is incongruent with the amount of work and the level of detail of
this annotation; CH: let's discuss that personally}

\section*{Conclusions} % what the paper is about
As an extension of the studyforrest dataset, we present an annotation of spoken
language in the two hours lasting ``research cut'' of the audio-visual movie
``Forrest Gump'' and its temporally aligned audio-description.
% what we did
We annotated the onset and offset of sentences, words and phonemes, and the
corresponding speaker's identity.
% what for
An additional tagging of each word's linguistic features and the public nature
of the dataset enable independent working groups to create sophisticated models
of hemodynamic activity correlating with speech-related events in a naturalistic
stimulus.
% results
Results of our dataset validating analysis that we run as a proof of concept
show that the annotation's content can indeed / in principle be used to
isolate/track speech-related networks in the human brain under life-like
conditions.
